\chapter{\LARGE{Training Videos}}

\begin{flushleft}
\large Related Open Access Lectures \& Tutorials (Up to Graduate-Level):
\end{flushleft}

\normalsize\begin{itemize}

  \item\textbf{Quantum Transport (Prof. Sergey Frolov):}\\
\url{https://youtube.com/playlist?list=PLtTPtV8SRcxjedflXwNPSI_fxvxwUCjsd}

  \item\textbf{Quantum Many-Body Physics (Prof. Luis Gregório Dias):}\\
\url{https://youtube.com/playlist?list=PL6FyrZIBwD8LMWizZW1FUN2dS_l44yuiy}

  \item\textbf{Quantum Matter (Prof. Steven Simon):}\\
\url{https://youtube.com/playlist?list=PLrNpJOaBSWSCrLUO_tuKa5l5YJl0JNr1z}

  \item\textbf{Quantum Computing Hardware \& Architecture (Prof. Hiu Yung Wong):}\\
\url{https://youtube.com/playlist?list=PLnK6MrIqGXsL1KShnocSdwNSiKnBodpie}

  \item\textbf{Quantum Hardware Series (Onri Jay Benally, QuantumGrad \& UMN):}\\
\url{https://youtube.com/playlist?list=PLD9iE8dbH_2W0ww1HL1gSskSYPcSlf6cd}

  \item\textbf{Circuit Quantum Electrodynamics \& Qubit Hamiltonian (Prof. Gerhard Kirchmair):}\\
\url{https://youtu.be/BAt2PFVQE3w}

  \item\textbf{Josephson Junctions \& SQUIDs (Prof. Kevin F. Kelly):}\\
\url{https://youtu.be/sNOpmTWlMwk}

  \item\textbf{Silicon Photonics \& Photonic Integrated Circuits Overview (Ghent University):}\\
\url{https://youtube.com/playlist?list=PLuNPwP_PUkFRcW4apwKHC7oXSTyV3zPbv}

  \item\textbf{Photonic Integrated Circuit Design (Ghent University):}\\
\url{https://youtu.be/Zcle3hNmblg}

  \item\textbf{Virtual Hands-On Nanofabrication (Dr. Jorg Scholvin):}\\
\url{https://youtu.be/01J8qKjcp0M}

  \item\textbf{Micro \& Nanofabrication (Prof. Chris Mack):}\\
\url{https://youtube.com/playlist?list=PLM2eE_hI4gSDjK4SiDbhpmpjw31Xyqfo}

  \item\textbf{Nanotechnology [Tools] (Duke University):}\\
\url{https://youtube.com/playlist?list=PLQcKpS4i0cAHES0sjJTXDZnWa3wtuixQl}

  \item\textbf{Qiskit Metal Overview, Gmsh \& ElmerFEM [Open-Source] (Diego Emilio Serrano \& Abeer Vaishnav):}\\
\url{https://youtu.be/84j3l_9fHko}

  \item\textbf{Pulse Sequence Shaping (Thomas Alexander, IBM):}\\
\url{https://www.youtube.com/watch?v=sMUPL8SR2oE&t=665s}

  \item\textbf{Physical Sciences \& Engineering Lectures (Dr. Jordan Edmunds):}\\
\url{https://www.youtube.com/@JordanEdmundsEECS/playlists}

  \item\textbf{Animated Physics Lectures (ZAP Physics):}\\
\url{https://www.youtube.com/@zapphysics/playlists}

  \item\textbf{More Animated Physics Lectures (Alexander Fufaev):}\\
\url{https://www.youtube.com/@universaldenker/playlists}

  \item\textbf{Even More Animated Physics Lectures (Dr. Elliot Schneider):}\\
\url{https://www.youtube.com/@PhysicswithElliot/playlists}

\item\textbf{Oscillator Tutorial (Afrotechmods):}\\
\url{https://youtu.be/aJAZHPqEUKU?si=a18oKNZBRZaG564o}

\item\textbf{The Beauty of LC Oscillations! (Sabin Mathew):}\\
\url{https://youtu.be/2_y_3_3V-so?si=viKn72TnpgGTPhfu}

  \item\textbf{Electronic Circuits (Julio Gonzalez):}\\
\url{https://youtube.com/playlist?list=PL0o_zxa4K1BV9E-N8tSExU1djL6slnjbL}

\end{itemize}

\space
\newpage

\begin{flushleft}
\large Miscellaneous:
\end{flushleft}

\normalsize\begin{itemize}

  \item\textbf{A Homemade Trapped Ion Quantum Computer (Yann Allain):}\\
\url{https://tinyurl.com/homemade-tr-ion}

  \item\textbf{Heidelberg DWL66+ LASER Lithography Training (University of Pennsylvania):}\\
\url{https://youtube.com/playlist?list=PLiihbHV9HgpWAcmgdpMGBkejcBhEzoKJO}

  \item\textbf{Electron-Beam Lithography (MIT.nano):}\\
\url{https://youtu.be/yJF9s2MJLLM}

  \item\textbf{Layout Editor Training (University of Pennsylvania):}\\
\url{https://youtube.com/playlist?list=PLiihbHV9HgpX_9m5Khz2wn-XaxM5-yErU}

  \item\textbf{KLayout Training (University of Waterloo):}\\
\url{https://youtube.com/playlist?list=PL12BCN5zxKhysQPbl0Fy0a6x0fiCPJZB-}

  \item\textbf{Oscilloscope Usage (GreatScottLab):}\\
\url{https://youtu.be/d58GzhXKKG8}

  \item\textbf{Harvard Architecture vs. von Neumann Architecture (Computer Science):}\\
\url{https://youtu.be/4nY7mNHLrLk}

  \item\textbf{Analog vs. Digital Computing (Derek Muller):}\\
\url{https://youtu.be/IgF3OX8nT0w?si=hWCan3S5Mx5NsdfE}

  \item\textbf{Flipper Zero Transceiver Hardware (Securiosity):}\\
\url{https://youtu.be/eYCMIYsP23k?si=U8L04s7Jun-RQV-L}

  \item\textbf{Understanding Radio Signals with Flipper Zero (TechAndFun):}\\
\url{https://youtu.be/zhg41DbxIEc?si=SG0jI6vYYOd1tfip}

  \item\textbf{Software Defined Radio (SDR) Tutorial (Andreas Spiess):}\\
\url{https://youtu.be/xQVm-YTKR9s?si=fD03k6WQYokeyx0-}

  \item\textbf{The Fetch-Execute Cycle (Tom Scott):}\\
\url{https://youtu.be/Z5JC9Ve1sfI}

  \item\textbf{Blender Basics for Scientists (Dr. Joseph G. Manion):}\\
\url{https://youtube.com/playlist?list=PLcKSD7d0T-HBmOH-NYYgMgVX1LZF72K-3}\\

\end{itemize}
